Template for manuscript

### 2024-12-11 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Work on manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R specifications
<<include = FALSE>>=
# knitr
library(knitr)
opts_chunk$set(fig.path = 'plots/p', 
               echo = FALSE, 
               results = 'hide',
               fig.height = 4.5,
               fig.align = "center",
               cache = TRUE)

@@

\begin{gather}
\alpha^{\ast}_{t} =
\begin{cases}
\alpha_{t-1} + \alpha_{t}, & \text{if } k_{t} = 0, \\
\frac{\alpha_{t}}{k_{t-1}} + \frac{-\exp{(-k_{t-1})}\alpha_{t}}{k_{t-1}} +
\exp{(-k_{t-1})}\alpha_{t-1}, & \text{otherwise},
\end{cases} \label{eq:sys1} \\
\alpha_{t} = \mathbf{X}_{t-1}\bm{\beta} + k_{t-1}O_{s,t-1}, \label{eq:sys2} \\
k_{t} = \frac{K^{\ast}_{t}\Delta t}{z_{t}}. \label{eq:sys3}
\end{gather}

@@

As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
data to estimate mixed layer depth. An initial approach to deal with that problem
was to investigate the effect of different mixed layer depths on the daily metabolism
estimates. For that purpose, we selected a few lakes for different monitoring
periods (2021, 2022, 2023) and assessed the impact of various, constant
mixed layer depths over time on the metabolism results.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R specifications
<<setup, include = FALSE>>=
# knitr
library(knitr)
opts_chunk$set(fig.path = 'plots/p', 
               echo = FALSE, 
               fig.align = "center",
               cache = TRUE)

@@

\begin{gather}
\alpha^{\ast}_{t} =
\begin{cases}
\alpha_{t-1} + \alpha_{t} & \text{if } k_{t} = 0, \\
\frac{\alpha_{t}}{k_{t-1}} + \frac{-\exp{(-k_{t-1})}\alpha_{t}}{k_{t-1}} +
\exp{(-k_{t-1})}\alpha_{t-1} & \text{otherwise},
\end{cases} \label{eq:sys1} \\
\alpha_{t} = \mathbf{X}_{t-1}\bm{\beta} + k_{t-1}O_{s,t-1}, \label{eq:sys2} \\
k_{t} = \frac{K^{\ast}_{t}\Delta t}{z_{t}}. \label{eq:sys3}
\end{gather}

@@

As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
data to estimate mixed layer depth. An initial approach to assess this issue
was to investigate the effect of different mixed layer depths on daily metabolism
estimates. For that purpose, we selected a few lakes for different monitoring
periods (2021, 2022, 2023). Notably, mixed layer
was held constant, which is rarely the case in reality.
In Figure~\ref{fig:sens}, an example of a sensitivity analysis for lake
B1P1 in 2021 is depicted. Plots A-C depict the daily GPP, R, and NEP estimates
for different mixed layer depths. For each mixed layer value, a separate model
was fitted, holding all other covariates equal.
Apparently, mixed layer depth substantially
impacts respiration, where a smaller mixed layer depth is associated with
higher (more negative) R. In contrast, GPP is barely affected by mixed
layer depth. Plots D-H show the input variables required to fit the metabolism
models, apart from mixed layer depth. Since mixed layer particularly
effects daily R estimates, careful consideration with regards to overcoming
this limitation is required. Notably, the effect of variation in mixed layer
depth was consistent across most lakes and monitoring periods

<<sensanal1, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE>>=
# Packages ad functions from Moritz Luehrig's paper
source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")

# Estimating lake metabolism with free-water oxygen
# See "report_analysis_metabolism_B3P3_2022" for further details
require(LakeMetabolizer)

# For plotting
require(GGally)

# Imputation of NAs for time-series (our NAs are due to outlier processing)
require(imputeTS)

# For Bayesian lake metabolism modeling
require(R2jags) # Also, installing JAGS is necessary under
# http://www.sourceforge.net/projects/mcmc-jags/files

require(ggpubr)
require(grid) # Arranging multiple plots
require(grDevices) # Saving png files

# This is our complete dataset of the sondes measurements 2021
# Measurement Interval: 2 minutes
all <- fread("../../project_21/data/processed_data_sondes/ponds_sonde_data_all.txt")

# Importing the metadata
# Wind and irradiation
# Measurement Interval: 1 hour, hourly averages
# Source: QAS_L automated weather station near Narsarsuaq
# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
# wind sensor height: 2.65 + 0.4 = ca 3.05m
meta <- fread("../../project_21/data/metadata_metabolism_analysis/metadata_2021.txt")

# Step 1: data formatting ------------------------------------------------------

# Select columns to keep from our time series
all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]

# Select Pond B1P1 (Treatment: Fish)
all <- subset(all, Pond == "B1P1")

# Rename
all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))

# Isolate the desired period (described in the introduction)
# Unfortunately, B1P1 had a huge data-gap so we can only estimate
# metabolism before (we have 4 complete days)
all <- all[c(121:3000),]

# choose desired period for the metadata
meta <- meta[c(1:97),]

# rename
meta <- setnames(meta,c("datetime", "dsr_cor", "wsp"))

meta <- meta %>%
  mutate(datetime = as.POSIXct(format(datetime, format = "%Y-%m-%d %H:01:00", tz = "UTC"), tz = "UTC"))

# Create a new inflated dataset with measurements every 2 minutes
# The hourly mean will be assigned to every observation (2min-interval) within that hour
meta_ext <- meta %>%
  complete(datetime = seq(from = min(datetime), to = max(datetime), by = "2 min"))

# Fill the missing wind speed and irradiation values with the corresponding hourly values using 'fill'
meta_ext <- meta_ext %>%
  fill(wsp, .direction = "up") %>%
  fill(dsr_cor, .direction = "up")

# Shift wind speed and irradiation one row up
meta_ext <- meta_ext %>%
  mutate(wsp = lead(wsp, default = last(wsp))) %>%
  mutate(dsr_cor = lead(dsr_cor, default = last(dsr_cor)))

# Ommit last row (not included in our timeseries)
meta_ext <- meta_ext[-nrow(meta_ext), ]

# Reset row names for the final result
rownames(meta_ext) <- NULL

# Step 2: merge the 2 datasets -------------------------------------------------
all <- merge(meta_ext, all, by = "datetime")

# Step 3: Missing data imputation ----------------------------------------------
# We need a complete ODO_mgL timeseries. Therefore we will impute the missing values
# here, with the package "imputeTS", which is specifically designed to impute time-series
# observations.

# 113 NAs (due to outlier processing)
# colSums(is.na(all))

# Make a timeseries object
ts <- ts(all$do.obs, frequency = 720)

# Impute with imputeTS
imp_all <- na_ma(ts) # use this function!
imp_all <- data.table(imp_all)
imp_all$datetime <- all$datetime

# Check for missing values in the imputed dataset
#sum(is.na(imp_all)) # No missing values anymore

# Check imputation by plotting the original and the imputed dataset
# plot(x = all$datetime, y = all$do.obs, type = "l", col = "blue", lwd = 2)
# lines(x = imp_all$datetime, y = imp_all$imp_all, type = "l",
#       col = rgb(1, 0, 0, alpha = 0.3), lwd = 2)
# The imputation worked very well!

# Replace original column with imputed column
all$do.obs <- imp_all$imp_all
# sum(is.na(all))

# Step 4: Model choice ---------------------------------------------------------
# Gas transfer coefficient model: kvachon()
# - needs wind speed, sensor height, and lake area

# Lake metabolism model: metab.bayesian()
# Most flexible model

# Step 5: Calculate k600 using the Cole method ---------------------------------

# This function needs specific column names
all$wnd <- all$wsp
all$wsp <- NULL

# Normalize wind to 10m sensor height
wind.scale <- wind.scale(all, wnd.z = 3.05)

all <- merge(all, wind.scale, by = "datetime")

all$wnd <- all$wnd_10
all$wnd_10 <- NULL

# Also only the 2 columns of interest, otherwise it gets confused
all.600 <- all[,c("datetime","wnd")]
k600.vachon <- k.vachon(all.600, lake.area = 2100)

# Merge
all <- merge(all, k600.vachon, by = "datetime")

# Step 6: Calculate gas-specific k600 ------------------------------------------

kgas <- k600.2.kGAS(all)

# Merge
all <- merge(all, kgas, by = "datetime")

# only keep k.gas
all$k600 <- NULL

# Step 7: Calculate dissolved oxygen saturated (do.sat) ------------------------

# I know that the sonde has do.sat measurements, but I have more faith
# in the authors of this paper to calculate a more accurate do.sat then the
# sonde-intern calculations.

o2.sat <- o2.at.sat(all[,c('datetime','wtr')])

# Merge
all <- merge(all, o2.sat, by = "datetime")

# Step 8: Derive photosynthetically active radiation (par) from shortwave irradiation (sw) ----
# Here, I take the downwelling shortwave irradiation (tilt corrected) from the
# QAS_L automated weather station a couple of kilometers away from Narsarsuaq
# It's the closest weather station measuring this parameter, that I could find.

# Derive par from sw
par <- sw.to.par(all, sw.col = "dsr_cor")
rownames(par) <- NULL

# Merge
all <- merge(all, par[,c("datetime", "par")], by = "datetime")

# Step 9: Calculate Actively mixed layer depth (z.mix) -------------------------

################################################################################
# The max depth of pond B1P1 is about 4m.
# According to the profiling plots, B1P1 had an actively mixed layer depth of
# about 2m on Sept 10 2021.
# We will fit a model with mixed layer depth of 0.5, 1, 2, and 3 meters for this pond.
# The ponds maximum depth is 4m.
################################################################################

# Set different mixed layer depths of sensitivity analysis
# For some reason, metab.bayesian does not recognize z.mix columns
# if they are not named "z.mix", hence I have to create a dataset for each z.mix
all2 <- all
all2$z.mix <- 0.5

all3 <-all
all3$z.mix <- 1

all4 <- all
all4$z.mix <- 2

all5 <- all
all5$z.mix <- 3

# Step 10: Fit model -----------------------------------------------------------

# Choose columns to keep
all2 <- all2[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
all3 <- all3[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
all4 <- all4[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
all5 <- all5[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]

capture.output({
  # Mixed layer depth 0.5m over the whole observation period
bayesian.res_0.5 <- metab(all2, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                      irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                      do.sat.name = "do.sat")

# Mixed layer depth 1m over the whole observation period
bayesian.res_1 <- metab(all3, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                        do.sat.name = "do.sat")

# Mixed layer depth 2m over the whole observation period
bayesian.res_2 <- metab(all4, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                        do.sat.name = "do.sat")

# Mixed layer depth 3m over the whole observation period
bayesian.res_3 <- metab(all5, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                        do.sat.name = "do.sat")
}, file = "NUL")
@

\vspace{0.5cm}
<<sensanal2, results='asis', fig.cap= "\\label{fig:sens}Example of a sensitivity analysis for mixed layer depth in lake B1P1, 2021. Figures A-C depict GPP, R, and NEP estimates for different mixed layer depths. Figures D-H depict time series of input variables needed for metabolism estimation.", fig.align='center',fig.height=7.5>>=
# Get standard deviations of estimates
bayesian.sd_0.5 <- attr(bayesian.res_0.5, "metab.sd")
bayesian.sd_1 <- attr(bayesian.res_1, "metab.sd")
bayesian.sd_2 <- attr(bayesian.res_2, "metab.sd")
bayesian.sd_3 <- attr(bayesian.res_3, "metab.sd")

# Create a date variable
bayesian.res_0.5$Date <- as.Date(paste(bayesian.res_0.5$year, "-", bayesian.res_0.5$doy, sep = ""), format = "%Y-%j")
bayesian.res_1$Date <- as.Date(paste(bayesian.res_1$year, "-", bayesian.res_1$doy, sep = ""), format = "%Y-%j")
bayesian.res_2$Date <- as.Date(paste(bayesian.res_2$year, "-", bayesian.res_2$doy, sep = ""), format = "%Y-%j")
bayesian.res_3$Date <- as.Date(paste(bayesian.res_3$year, "-", bayesian.res_3$doy, sep = ""), format = "%Y-%j")

# Select columns to keep
bayesian.res_0.5 <- bayesian.res_0.5[,c("Date", "GPP", "R", "NEP")]
bayesian.res_1 <- bayesian.res_1[,c("Date", "GPP", "R", "NEP")]
bayesian.res_2 <- bayesian.res_2[,c("Date", "GPP", "R", "NEP")]
bayesian.res_3 <- bayesian.res_3[,c("Date", "GPP", "R", "NEP")]

# Create a date variable
bayesian.sd_0.5$Date <- as.Date(paste(bayesian.sd_0.5$year, "-", bayesian.sd_0.5$doy, sep = ""), format = "%Y-%j")
bayesian.sd_1$Date <- as.Date(paste(bayesian.sd_1$year, "-", bayesian.sd_1$doy, sep = ""), format = "%Y-%j")
bayesian.sd_2$Date <- as.Date(paste(bayesian.sd_2$year, "-", bayesian.sd_2$doy, sep = ""), format = "%Y-%j")
bayesian.sd_3$Date <- as.Date(paste(bayesian.sd_3$year, "-", bayesian.sd_3$doy, sep = ""), format = "%Y-%j")

# Select columns to keep
bayesian.sd_0.5 <- bayesian.sd_0.5[,c("Date", "GPPsd", "Rsd", "NEPsd")]
bayesian.sd_1 <- bayesian.sd_1[,c("Date", "GPPsd", "Rsd", "NEPsd")]
bayesian.sd_2 <- bayesian.sd_2[,c("Date", "GPPsd", "Rsd", "NEPsd")]
bayesian.sd_3 <- bayesian.sd_3[,c("Date", "GPPsd", "Rsd", "NEPsd")]

bayesian.merge_0.5 <- merge(bayesian.res_0.5, bayesian.sd_0.5, by = "Date")
bayesian.merge_1 <- merge(bayesian.res_1, bayesian.sd_1, by = "Date")
bayesian.merge_2 <- merge(bayesian.res_2, bayesian.sd_2, by = "Date")
bayesian.merge_3 <- merge(bayesian.res_3, bayesian.sd_3, by = "Date")

# create Z.mix variable identifier
bayesian.merge_0.5$z.mix <- "0.5m"
bayesian.merge_1$z.mix <- "1m"
bayesian.merge_2$z.mix <- "2m"
bayesian.merge_3$z.mix <- "3m"

# Merge
bayesian.merge.all <- rbind(bayesian.merge_0.5, bayesian.merge_1,
                            bayesian.merge_2, bayesian.merge_3)

# Step 11: Visualize the results -----------------------------------------------

# GPP
p1 <- ggplot(data = bayesian.merge.all, aes(x = Date, y = GPP, linetype = z.mix)) + 
  theme_light() +
  geom_line() +
  geom_errorbar(aes(ymin = GPP - GPPsd, ymax = GPP + GPPsd), width = 0.12,
                linetype = "solid") +
  scale_linetype_manual(
    values = c("0.5m" = "solid", "1m" = "dashed", "2m" = "dotted", "3m" = "dotdash")
  ) +
  ylab(expression(paste("GPP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")"))) +
  labs(linetype = "Mixed layer depth")

# R
p2 <- ggplot(data = bayesian.merge.all, aes(x=Date, y=R, linetype=z.mix)) + theme_light() +
  geom_line() +
  geom_errorbar(aes(ymin = R-Rsd, ymax = R+Rsd), width = 0.12,
                linetype = "solid") +
  scale_linetype_manual(
    values = c("0.5m" = "solid", "1m" = "dashed", "2m" = "dotted", "3m" = "dotdash")
  ) +
  ylab(expression(paste("R (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")"))) +
  labs(linetype = "Mixed layer depth")

# NEP
p3 = ggplot(data = bayesian.merge.all, aes(x=Date, y=NEP, linetype=z.mix)) + theme_light() +
  geom_line() +
  geom_errorbar(aes(ymin = NEP-NEPsd, ymax = NEP+NEPsd), width = 0.12,
                linetype = "solid") +

  scale_linetype_manual(
    values = c("0.5m" = "solid", "1m" = "dashed", "2m" = "dotted", "3m" = "dotdash")
  ) +
  ylab(expression(paste("NEP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")"))) +
  labs(linetype = "Mixed layer depth")

# Plots of ecosystem parameters
p4 = ggplot((all)) + theme_light() +
  geom_line(aes(y=do.obs, x=datetime)) +
  rremove("xlab") +
  ylab(expression(paste("DO (mg L",NULL^-1,")")))

p5 = ggplot((all)) + theme_light() +
  geom_line(aes(y=do.sat, x=datetime)) +
  rremove("xlab") +
  ylab(expression(paste("DO.sat (mg L",NULL^-1,")")))

p6 = ggplot((all)) + theme_light() +
  geom_line(aes(y=wtr, x=datetime)) +
  rremove("xlab") +
  ylab("Temperature (°C)")

p7 = ggplot((all)) + theme_light() +
  geom_line(aes(y=par, x=datetime)) +
  rremove("xlab") +
  ylab(expression(paste("PAR (",mu,"mol m",NULL^-2," s",NULL^-1,")")))

p8 = ggplot((all)) + theme_light() +
  geom_line(aes(y=k.gas, x=datetime)) +
  rremove("xlab") +
  ylab(expression(paste("Gas transfer coefficient (m",NULL^-1,")")))

fig2 <- ggarrange(p1 + rremove("xlab"), p2 + rremove("xlab"), p3 + rremove("xlab"),
                  p4 + rremove("xlab"), p5 + rremove("xlab"), p6 + rremove("xlab"),
                  p7 + rremove("xlab"), p8 + rremove("xlab"), nrow=4, ncol = 2,
                  common.legend = TRUE, legend = "bottom",
                  labels = c("A", "B", "C", "D", "E", "F", "G", "H"),label.x = -0.045,
                  align = "hv")

fig2 <- annotate_figure(fig2) +
  theme(plot.margin = margin(t = 5, r = 12, b = 5, l = 12))
print(fig2)
@
\vspace{0.5cm}

### 2024-12-11 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.tex
Work on manuscript

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Wed Dec 11 09:32:21 2024
\begin{table}[ht]
\centering
\caption{Lakes included in the experiment, along with treatment
                and general characteristics.} 
\label{tab:lakes}
\begin{tabular}{lllllll}
  \toprule
Lake & Treatment & Latitude (°N) & Longitude (°E) & Altitude (m) & Area (hectare) & Maximum Depth (m) \\ 
  \midrule
B1P1 & Fish & 61.15338 & -45.57081 & 272 & 0.21 & 4.00 \\ 
  B2P2 & Fish & 61.12299 & -45.55988 & 255 & 0.50 & 3.00 \\ 
  B3P3 & Fish & 61.13385 & -45.57556 & 258 & 0.30 & 5.00 \\ 
  B2P3 & Fish & 61.12275 & -45.55696 & 261 & 0.41 & 4.25 \\ 
  B3P1 & Fish & 61.13130 & -45.51195 & 180 & 0.40 & 2.00 \\ 
  B3P2 & Fish & 61.12788 & -45.51031 & 201 & 0.53 & 4.50 \\ 
  B1P4 & No Fish & 61.16552 & -45.56801 & 304 & 0.44 & 2.20 \\ 
  B2P4 & No Fish & 61.12192 & -45.55497 & 261 & 0.51 & 7.00 \\ 
  B3P0 & No Fish & 61.13210 & -45.51416 & 177 & 0.81 & 4.00 \\ 
  ERL85 & No Fish & 61.14171 & -45.59328 & 120 & 1.82 & 8.00 \\ 
  ERL122 & No Fish & 61.14182 & -45.53623 & 111 & 1.10 & 5.00 \\ 
  ERL152 & No Fish & 61.14646 & -45.59235 & 156 & 0.73 & 4.50 \\ 
   \bottomrule
\end{tabular}
\end{table}

@@

As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
data to estimate mixed layer depth. An initial approach to deal with that problem
was to investigate the effect of different mixed layer depths on the daily metabolism
estimates. For that purpose, we selected a few lakes for different monitoring
periods (2021, 2022, 2023) and assessed the impact of various, constant
mixed layer depths over time on the metabolism results.

>>>>

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Wed Dec 11 10:21:21 2024
\begin{table}[ht]
\centering
\caption{Lakes included in the experiment, along with treatment
                and general characteristics.} 
\label{tab:lakes}
\begin{tabular}{lllllll}
  \toprule
Lake & Treatment & Latitude (°N) & Longitude (°E) & Altitude (m) & Area (hectare) & Maximum Depth (m) \\ 
  \midrule
B1P1 & Fish & 61.15338 & -45.57081 & 272 & 0.21 & 4.00 \\ 
  B2P2 & Fish & 61.12299 & -45.55988 & 255 & 0.50 & 3.00 \\ 
  B3P3 & Fish & 61.13385 & -45.57556 & 258 & 0.30 & 5.00 \\ 
  B2P3 & Fish & 61.12275 & -45.55696 & 261 & 0.41 & 4.25 \\ 
  B3P1 & Fish & 61.13130 & -45.51195 & 180 & 0.40 & 2.00 \\ 
  B3P2 & Fish & 61.12788 & -45.51031 & 201 & 0.53 & 4.50 \\ 
  B1P4 & No Fish & 61.16552 & -45.56801 & 304 & 0.44 & 2.20 \\ 
  B2P4 & No Fish & 61.12192 & -45.55497 & 261 & 0.51 & 7.00 \\ 
  B3P0 & No Fish & 61.13210 & -45.51416 & 177 & 0.81 & 4.00 \\ 
  ERL85 & No Fish & 61.14171 & -45.59328 & 120 & 1.82 & 8.00 \\ 
  ERL122 & No Fish & 61.14182 & -45.53623 & 111 & 1.10 & 5.00 \\ 
  ERL152 & No Fish & 61.14646 & -45.59235 & 156 & 0.73 & 4.50 \\ 
   \bottomrule
\end{tabular}
\end{table}

@@

As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
data to estimate mixed layer depth. An initial approach to assess this issue
was to investigate the effect of different mixed layer depths on daily metabolism
estimates. For that purpose, we selected a few lakes for different monitoring
periods (2021, 2022, 2023). Notably, mixed layer
was held constant, which is rarely the case in reality.
In Figure~\ref{fig:sens}, an example of a sensitivity analysis for lake
B1P1 in 2021 is depicted. Plots A-C depict the daily GPP, R, and NEP estimates
for different mixed layer depths. For each mixed layer value, a separate model
was fitted, holding all other covariates equal.
Apparently, mixed layer depth substantially
impacts respiration, where a smaller mixed layer depth is associated with
higher (more negative) R. In contrast, GPP is barely affected by mixed
layer depth. Plots D-H show the input variables required to fit the metabolism
models, apart from mixed layer depth. Since mixed layer particularly
effects daily R estimates, careful consideration with regards to overcoming
this limitation is required. Notably, the effect of variation in mixed layer
depth was consistent across most lakes and monitoring periods

\vspace{0.5cm}
\begin{figure}

{\centering \includegraphics[width=\maxwidth]{plots/psensanal2-1}

}

\caption{\label{fig:sens}Example of a sensitivity analysis for mixed layer depth in lake B1P1, 2021. Figures A-C depict GPP, R, and NEP estimates for different mixed layer depths. Figures D-H depict time series of input variables needed for metabolism estimation.}\label{fig:sensanal2}
\end{figure}

\vspace{0.5cm}
